Relative Stable Maps in Genus One via Central Alignments

### 2018-02-08 genus-one-relative-maps.tex
Changed code

\section{The space of relative centrally aligned maps}
\noindent Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by first considering the  Cartesian diagram
\bcd
\tVZc(X,\beta)\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & \M{1}{n}{X}{\beta}\ar[d] \\
\MM_{1,n}^{\rm{ctr}}\ar[r] & \MM_{1,n}^{\dagger}
\ecd
so that objects of $\tVZc(X,\beta)$ consist of
\begin{enumerate}
\item a centrally aligned curve $(C,M_C,\delta)$;
\item a stable map $f\colon C \to X$;
\end{enumerate}
subject to the condition that the contraction radius $\delta$ of the central alignment is equal to $\delta_f$, the contraction radius of the stable map $f$. \marginpar{what is the contraction radius of $f$? I think to be precise we need to say $\delta=\lambda(v)$ for $v$ such that $f$ contracts any component of $C$ closer to the circuit than $C_v$, while it has positive degree on $C_v$...} We then define
\begin{equation*} \VZc(X,\beta) \subseteq \tVZc(X,\beta) \end{equation*}
to be the closed substack consisting of maps satisfying the \emph{factorisation condition}, namely that the map $f\colon C\to X$ factors through the associated contraction to a Smyth curve, i.e. there exists a map $\bar{f}$ making the following square commute:
\bcd
\widetilde C\ar[r]\ar[d] & \overline C\ar[d,"\bar f" left,dotted] \\
C\ar[r,"f"] & X
\ecd
One should think of the factorisation condition as identifying the main component of the moduli space.

@@

\begin{lem}\label{Nice locus is irreducible}
The nice locus $\VZcrel(\PP^N|H,d)^{\circ}$ is irreducible.
\end{lem}
\begin{proof}
By definition the contraction radius $\delta$ is compatible with the map, i.e. the subcurve $C_0\subseteq C$ where $\lambda<\delta$ is equal to the maximal connected genus one subcurve contracted by $f$.\marginpar{this is FALSE! I guess we may say $\delta=\lambda(v)$ for some $v$ and there is only one $v$ in this case} Hence when the source curve is irreducible we must have $\delta=0$, and we see that the central alignment on $C$ is uniquely and trivially determined. Thus to specify a point in the nice locus we only need to specify the source curve $C$ (as a scheme) and the map $f$. A parametrisation can be given from the vector bundle:\marginnote{I'm sure there's a simpler way to say this - Navid}
\[ \operatorname{Vb}\left(\pi_*\OO_{\mathcal E}(\sum_{j=n+1}^{n+\delta}\sigma_j)\oplus\pi_*\OO_{\mathcal E}(\sum_{j=1}^{n+\delta}\sigma_j)^{\oplus r}\right) \quad \text{on} \quad \mathcal{M}_{1,n+\delta}\]
where $\pi\colon\mathcal E\to\mathcal M$ is the universal curve and $\delta=d-\sum\alpha_i$.
\end{proof}

>>>>

\section{The space of relative centrally aligned maps}
\noindent Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by first considering the  Cartesian diagram
\bcd
\tVZc(X,\beta)\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & \M{1}{n}{X}{\beta}\ar[d] \\
\MM_{1,n}^{\rm{ctr}}\ar[r] & \MM_{1,n}^{\dagger}
\ecd
so that objects of $\tVZc(X,\beta)$ consist of
\begin{enumerate}
\item a centrally aligned curve $(C,M_C,\delta)$;
\item a stable map $f\colon C \to X$;
\end{enumerate}
subject to the condition that the contraction radius $\delta$ of the central alignment is equal to $\delta_f$, the contraction radius of the stable map $f$. We then define
\begin{equation*} \VZc(X,\beta) \subseteq \tVZc(X,\beta) \end{equation*}
to be the closed substack consisting of maps satisfying the \emph{factorisation condition}, namely that the map $f\colon C\to X$ factors through the associated contraction to a Smyth curve, i.e. there exists a map $\bar{f}$ making the following square commute:
\bcd
\widetilde C\ar[r]\ar[d] & \overline C\ar[d,"\bar f" left,dotted] \\
C\ar[r,"f"] & X
\ecd
One should think of the factorisation condition as identifying the main component of the moduli space.

@@

\begin{lem}\label{Nice locus is irreducible}
The nice locus $\VZcrel(\PP^N|H,d)^{\circ}$ is irreducible.
\end{lem}
\begin{proof}
By definition the contraction radius $\delta$ is compatible with the map, i.e. the subcurve $C_0\subseteq C$ where $\lambda<\delta$ is equal to the maximal connected genus one subcurve contracted by $f$. Hence when the source curve is irreducible we must have $\delta=0$, and we see that the central alignment on $C$ is uniquely and trivially determined. Thus to specify a point in the nice locus we only need to specify the source curve $C$ (as a scheme) and the map $f$. A parametrisation can be given from the vector bundle:\marginnote{I'm sure there's a simpler way to say this - Navid}
\[ \operatorname{Vb}\left(\pi_*\OO_{\mathcal E}(\sum_{j=n+1}^{n+\delta}\sigma_j)\oplus\pi_*\OO_{\mathcal E}(\sum_{j=1}^{n+\delta}\sigma_j)^{\oplus r}\right) \quad \text{on} \quad \mathcal{M}_{1,n+\delta}\]
where $\pi\colon\mathcal E\to\mathcal M$ is the universal curve and $\delta=d-\sum\alpha_i$.
\end{proof}
